---
title: "Dplyr package"
output:
  pdf_document: default
  html_notebook: default
---

# Dplyr
```{r}
install.packages("dplyr")
library(dplyr)
```
- Simple “verbs” functions that correspond to the most common data manipulation tasks
- Constrain options
- Fast

# Arrange
```{r}
info <- read.table("info.csv",sep=",",header=TRUE)
colnames(info)
sorted <- arrange(info,desc(Temperature,Unemployment))
head(info)
summary(info)
```


# Select
```{r}
selected<-select(info,Unemployment,Temperature)
selected
```

# Distinct - find unique values in a table, similar to unique()
```{r}
distinct(info, Store)
distinct(info, IsHoliday)
```

# Filter
```{r}
filtered<-filter(selected,Temperature>=90)
filtered
```

# Mutate - create a new column by manipulating existing columns
```{r}
real<-mutate(info,Fuel_Price_Real=Fuel_Price/CPI*100)
real
```

# Group_by, similar to tapply
# Summarise - summary statistics

# Use pop operator to do all of the above in a batch
```{r}
info %>%
  select(Unemployment,Temperature) %>%
  arrange(desc(Temperature)) %>%
  filter(Temperature>=90) %>%
  View

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
