---
title: "caret"
author: "Yue Jin"
date: "11/8/2017"
output:
  pdf_document: default
  html_document: default
---
The caret package is a set of tools for building machine learning models in R. The name “caret” stands for Classification And REgression Training. As the name implies, the caret package gives you a toolkit for building classification models and regression models. Moreover, caret provides you with essential tools for:

There are many different modeling functions in R. Some have different syntax for model training and/or prediction. The package started off as a way to provide a uniform interface the functions themselves, as well as a way to standardize common tasks (such parameter tuning and variable importance).


```{r setup, include=FALSE}
data(mtcars)
require(caret)
```


One of the primary tools in the package is the train function which can be used to
- evaluate, using resampling, the effect of model tuning parameters on performance
- choose the “optimal” model across these parameters
- estimate model performance from a training set


```{r cars}
summary(mtcars)
ind<-sample(1:nrow(mtcars),0.75*nrow(mtcars))
ind<-createDataPartition(
  y=mtcars$wt,
  ## the outcome data are needed
  p = .75,
  ## The percentage of data in the training set
  list = FALSE
  ## The format of the results
  )
mtcars_train<-mtcars[ind,]
mtcars_test<-mtcars[-ind,]
# create training index

# train(formula, dataset, method)
mtcarsFit <- train(mpg ~ wt,
                         mtcars_train,
                         method = "lm",
                         ## Center and scale the predictors for the training
                         preProc = c("center", "scale")
                        )
c <- coef(mtcarsFit$finalModel)[1]
b <- coef(mtcarsFit$finalModel)[2]

```

Other customization:
However, we would probably like to customize it in a few ways:
- tuning grid/parameter search method
- the type of resampling used. The simple bootstrap is used by default. We can use cross validation
- the methods for measuring performance. If unspecified, overall accuracy and the Kappa statistic are computed. For regression models, root mean squared error and R2 are computed.

# Prediction
```{r}
pred <- predict(mtcarsFit, newdata = mtcars_test)
pred
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
