---
title: "ggplot for R Open Lab"
author: "Yue Jin"
date: "10/24/2017"
output: html_document
---

## What ggplot2 can do and can not do?
* gg stands for grammar of graphics. ggplot2 is consistent with grammar of graphics. 
* ggplot cannot do 3D graphic and interactive graphics. (use plotly along with ggplot)

## Grammar of Graphics

A grammar of graphics provides a structure to combine graphical elements into figures that display data in a meaningful way. Building blocks of a graph include:
* data
* coordinate system: cartesian, polar
* geometric object: marks you used to represent data (points, line, bins)
* aesthetic mapping: visual property of the objects in the plot, anything you can see (location, shape, size)
* statistical transformations: mean, median

## How does ggplot work?
* Every graph is composed of a data set, a coordinate system and a set of geoms that represent data points
* To display data values, map variables in the data set to aesthetic properties of the geom like size, color, and x and y locations.

## Setup
```{r}
if(!require("ggplot2")){
  install.packages("ggplot2")
}
if(!require("ggthemes")){
  install.packages("ggthemes")
}

library(ggplot2)
library(ggthemes)
```

## Example1
We would like to plot carat vs price in the diamonds dataset. No transformation is needed. We would liek to pepresent it by points

### Recall:
- geom is a geometrical object used to represent data in a plot: points, lines, bins
- aes is the visual property of the objects in the plot. i.e. something you can see, examples: position, shape, size, color etc

```{r}
a<-ggplot(diamonds, aes(x=carat, y=price))+
    geom_point()+
    ggtitle("Diamond")
a
```

We can use two aesthetic properties to represent one feature of the data so as to emphasize it. Here we decorate the point using different colors according to its carat. 
```{r}
b<-a + facet_wrap(~cut)
b
c<-ggplot(diamonds)+
    geom_point(aes(x=carat, y=price,color=cut))+
    ggtitle("Diamond")
c
```


Personalize your plot
```{r}
d<-c+theme_economist() + scale_colour_economist() +
  scale_y_continuous(position = "right")
d
```

Add another layer of our prediction/calculated statistics
```{r}
pred <- predict(lm(price ~ carat, data = diamonds))
e<-a + 
  geom_point(aes(colour = carat)) +
  geom_line(aes(y=pred))
e
```

Our prediction doesn't look good.
To better see the pattern of the data, we can use geom_smooth
By default, the ggplot chooses a method to fit the data based on the size of the data and then draw 95% confidence level interval for predictions
```{r}
f<-a + 
  geom_point(aes(colour = carat)) +
  geom_smooth()+
  theme_economist()

ggplot(diamonds,aes(x=carat, y=depth))+
  geom_line()+
  geom_smooth()+
  theme_economist()

```

## Example 2

Stack bar plot
```{r}
ggplot(diamonds, aes(x = clarity, fill = cut)) +
  geom_bar() +
  scale_fill_brewer() +
  theme_economist()+
  ggtitle("Diamond")
```

## Example 3

Violin Plot
```{r}
ggplot(diamonds,aes(x=cut,y=price))+
  geom_violin(scale="area",aes(color=cut))+
  theme_solarized() +
  scale_colour_solarized("blue")+
  ggtitle("Price-Cut Violin Plot")
```

## Example 4

Plot two datasets together
```{r}
df1<-diamonds[,c("cut","price")]
df2<-diamonds$cut

ggplot()+
  geom_violin(data=df1,aes(x=cut,y=price))+
  geom_bar(data=data.frame(table(df2)),stat="identity",aes(x=df2,y=Freq))+
  theme_solarized() +
  scale_colour_solarized("blue")+
  ggtitle("Price-Cut Violin Plot")
```

