---
title: "openLab_02/01"
author: "Yue Jin"
date: "02/01/2017"
output:
  html_document: default
  pdf_document: default
---
## Why do we use R Markdown?
R Markdown provides a reproducible document framework for data science, and you can use a single R Markdown file to 

* save and execute codes
* generate high quality reports that can be shared with an audience; make formatting much easier
    + for example: $\hat{y_i}$ =  $\hat{\beta}_0$+ $\hat{\beta}_1{x_i}$
* interactive content: shiny app

## Create a R Markdown file
* insert chunk (Windows: Ctrl + Alt + I Mac: Cmd + Option + I)
* chunk options
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

* plot
```{r echo=FALSE}
one <- c(1:50)
four <- (1:50)*0.8+0.3
plot(four~one)
plot(four~one, xlim=c(1,50), ylim=range(four), pch=10)
plot(four~one, xlim=range(one), ylim=range(four), pch=16,col=3)
title('Random Plot')
abline(a=0,b=1,col=1)

library(DAAG)
data(tinting)
attach(tinting)
colnames(tinting)
densityplot(~age|sex*target)
xyplot(csoa ~ it|sex*agegp, data=tinting)
table(agegp, sex)


```


## Different output formats
* Notebook
* Presentation
* Dashboard
* Interactive documents: shiny, htmlwidgets
